<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2014-09-03 ants2015build.Rmd
WIP: regular update

<div align="center"><img width="2500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>

@@

Only change to the command call is an additional '-c WM[7]' which means "combine
the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."

>>>>

<div align="center"><img width="3500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>

@@

Only change to the command call is an additional '-c WM[7]' which means "combine
the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
# Wrap-up & Conclusions
